A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-15 doc/draft-01-stokes/03analysis2.tex
Updating section 3

In this section, we discuss how integral equations.
can be used to compute to the Stokes eigenvalues.
%
We closely follow the approach developed by Zhao and Barnett
for computing the Laplace eigenvalues.
%
Their work computes the Laplace eigenvalues using the following
steps: 1) represent the solution 
as a layer potential with 
an unknown density, and choose the representation such that
you get a second kind integral equation for the unknown density;
2) establish that the intergral equation is not invertible 
exactly for the Dirichlet eigenvalues for Laplace's equation;
3) prove that the zeros of the Fredholm determinant 
(when the compact operator is in trace class) 
line up with the Dirichlet eigenvalues; 
4) and finally, show that when the integral equation
is discretized using a Nystr\"{o}m method, the zeros of 
the determinant 
of the discrete linear system 
converge exponentially
to the zeros of the Fredholm determinant.

In this section, we adapt their approach for computing the 
Dirichlet eigenvalues for Stokes equation. 
%
We first develop some uniqueness
results for the osciallatory Stokes PDE which are essential
for establishing step 2 of the Zhao-Barnett approach.
To the best of our knowledge, the uniqueness results, particularly
for exterior domains are new results.

In order to prove the uniqueness results, we follow the 
structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
for the scalar Helmholtz equation.
%
First, we define the interior boundary value problems
of interest, which is straightforward.
%
For the exterior problems, we introduce a radiation condition
for the equations and establish that, under certain assumptions,
the standard layer potentials satisfy the radiation condition.
%
We then define well-posed versions of the
exterior boundary value problems which incorporate the
radiation condition.
%
Then we derive a number of uniqueness
results for the boundary value problems.
%
Along with the Fredholm alternative, these uniqueness
results are sufficient to derive the invertibility of appropriate
integral equations for a number of boundary value problems
on simply and multiply connected domains.

Once the equivalence between the non-invertibility
of the second kind integral equation and Dirichlet eigenvalues
for Stokes equations is established,
the details of how the Fredholm determinant can be used as a
numerical tool for computing the Stokes eigenvalues
follows in a straightforward manner from the results 
in Zhao and Barnett~\cite{zhao2015robust}. 
We reproduce the relevant results from their work applied 
in this context for completeness.

@@

Let $\Omega$ be a bounded domain with $C^2$ boundary
denoted by $\Gamma$.
The standard Dirichlet boundary problem specifies the
velocity of the fluid on the boundary, i.e.

@@

Let $\bsigma$ denote the stress tensor associated with
field $(\bu,p)$. 
Specifying the surface traction, $\bt = \bsigma \cdot \bnu$,
on the boundary gives the standard Neumann boundary value
problem, i.e.

@@

\begin{proposition}
The oscillatory Stokeslet, as in \eqref{eq:ostokeslet}, satisfies
the radiation condition in Definition \ref{def:radcond}.
Assuming that a density $\bmu$ is integrable and satisfies
$\int_\Gamma \bmu\cdot \bnu dS = 0$, where $\bnu$ denotes the
outward normal to the curve $\Gamma$, the oscillatory Stokes
double layer potential $\bD\bmu$, as in \eqref{eq:doublelayer},
also satisfies the radiation condition.
\end{proposition}

\begin{proof}
Consider the Stokeslet induced by an arbitrary charge
$k^2 \bpsi$ at the origin. Let $r = |\xx|$,
$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have

@@

\begin{definition}[Exterior Dirichlet problem]
  \label{def:dir_exterior}
  Let $\ff \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:dir_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bu &= \ff \quad \bx \in \Gamma \, 
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}
\begin{definition}[Exterior Neumann problem]
  \label{def:neu_exterior}  
  Let $\bg \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt &= \bg \quad \bx \in \Gamma \,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

@@

\begin{thrm}
  Let $\Omega$ be a bounded domain and suppose that
  $\Im (k) > 0$. Then both the interior
  Dirichlet and Neumann boundary value problems have
  unique solutions.
\end{thrm}
\begin{proof}
  A couple applications of the divergence theorem establish
  that
  \begin{equation} \label{eq:greenlike}
    \int_\Omega |2\be(\bu)|^2 - \overline{k}^2 |\bu|^2 \, dV
    = \int_\Gamma \bu \cdot \overline{\bt} \, dS \; . 
  \end{equation}
  Suppose that either $\bu = 0$ or $\bt = 0$ on $\Gamma$.
  Then, the right hand side of \cref{eq:greenlike} is
  zero. Taking the real and imaginary parts of \cref{eq:greenlike},
  it is clear that $\bu \equiv 0$.
\end{proof}

@@

In the next lemma, we prove the analogue of Rellich's lemma for the
oscillatory Stokes equation. 
\begin{lem}
  \label{lem:rellich}
    Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose that $\bu$ satisfies the oscillatory Stokes equation in
  $E$ and that 
\begin{equation}
\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
\, . \label{eq:decayatinf}
\end{equation}
Then each component of $\bu$ is harmonic in $E$.
\end{lem}
\begin{proof}
We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
oscillatory biharmonic equation in $E$, i.e.
\begin{equation}
\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
\end{equation}
For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
j=1,2 \, . \nonumber
\end{equation}
Using Parseval's identity then
\begin{equation}
\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
|a_{2,n}(r)|^2 \, . \nonumber
\end{equation}
Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
\begin{equation}
\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
\end{equation}
Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
the functions $a_{j,n}$ are linear combinations of 
\begin{equation}
r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
n\neq 0 \, , \nonumber
\end{equation}
and
\begin{equation}
1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, ,  \nonumber
\end{equation} 
where $H_{n}^{1,2}(\cdot)$ are the Hankel functions of the first and
second kind of order $n$.
Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$ must be zero. 
Thus, 
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
\, , \nonumber
\end{equation}
for sufficiently large $r$.
Finally, by \cref{cor:analytic}, $\bu$ is
analytic in $E$. Therefore, each $u_j$ is harmonic
throughout $E$.
\end{proof}
\begin{remark} \label{rmk:harmu}
  Note that if $\bu$ satisfies the assumptions
  of~\cref{lem:rellich}, then each component is harmonic
  and thus $\bu$ satisfies
\begin{align}
k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
\nabla \cdot \bu &= 0 \, . \nonumber
\end{align}
Taking the inner product of~\cref{eq:massconsred} with $\nabla^{\perp}$,
we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
and $\nabla \cdot \bu = 0$, i.e. $u_1 - i u_2$ is analytic.
\end{remark}
\begin{remark}
Note that in Rellich's lemma $\bu$ need not be a radiating solution. 
All that is assumed of $\bu$ is that it satifies the PDE in $E$.
\end{remark}

@@

\begin{proof}
Since $\bu = 0$ on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{equation}
\lim_{r\to\infty}
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
dV = 0 \nonumber
\end{equation} 
In particular, this implies that
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, . \nonumber
\end{equation}
Thus, the conditions for $\bu$ in Rellich's lemma (~\cref{lem:rellich})
are satisfied, and each component of $\bu$ is a harmonic function
with $\bu \to 0$ as $r \to \infty$. Furthermore, since $\bu=0$ on
$\Gamma$, by the uniqueness of solutions to the
Dirichlet problem for Laplace's equation
on exterior domains, we conclude that $\bu \equiv 0$ in $E$.
\end{proof}

@@

\begin{proof}
Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = i\eta \bu$
on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{align*}
0 &=
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
&= 
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad + 2 \left( (k_{1}\eta_{1} + k_{2}\eta_{2}) \int_{\Gamma} |\bu|^{2} dS  \right)
\, .
\end{align*}
Because all of the quantities in the last expression above are
nonnegative, we have that
\begin{equation}
  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, ,
  \nonumber
\end{equation}
and the estimate
\begin{equation}
\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} dS \to 0 \, . \nonumber
\end{equation}
The last equation implies the conditions for~\cref{lem:rellich}
are satisfied, from which we conclude that the components
of $\bu$ are harmonic in $E$. 
Thus, the components of $\bu$ satisfy
\begin{equation}
\Delta u_{j}=  0 \quad \xx \in E \quad \text{and} \quad
u_{j} = 0 \quad \xx \in \Gamma \, , \nonumber
\end{equation}
for $j=1,2$.
Then $\bu \equiv 0$ follows from the uniqueness of solutions to the 
Dirichlet problem for Laplace's equation.
\end{proof}

@@

We analyze two different representations for the Dirichlet problem---
when the velocity is represented using a double layer potential,
i.e. setting $u=\bD \bmu$, and when the velocity
is represented using a mixed layer potential,
i.e. setting $u=(i\eta \bS + \bD)\bmu$, where in both cases $\bmu$ 
is the unknown density to be solved for. 
Even though both reprensentations result in a second kind
Fredholm integral equation for the Dirichlet problem,
the spectral properties of these representations are very
different based on the genus of the domain.
We analyze the double layer potential representation 
in~\cref{subsec:dlanalysis}
and the mixed layer potential representation in~\cref{subsec:mixedanalysis}.

\begin{remark}
The analysis of integral equations for the oscillatory Stokes
equation and the correspondance betweeen its null spaces and the eigenvalues
of Stokes equation is analogous to a similar analysis carried out
for integral equations for Helmholtz equation and the eigenvalues
for the Laplace equation in~\cite{zhao2015robust}.
$\bu$ plays the role of the Dirichlet data, and $\bt$ plays the role
of the Neumann data. 
Once the Green's representation and uniqueness results for the 
the oscillatory Stokes equation have been established,
the remainder of the analysis of the integral equations
is in spirit identical to the analysis presented in~\cite{zhao2015robust}.
\end{remark}

\subsubsection{Double layer reprensentation}
\label{subsec:dlanalysis}
Suppose that the solution to the Dirichlet problem using
a double layer potential defined on $\Gamma$, i.e.
setting $\bu = \bD \bmu$ for
an unknown density $\bmu$. 
Substituting this representation
into the Dirichlet boundary condition and applying
\cref{lem:jump-conds}, we obtain

\begin{equation}
  (\cI - 2\cD_{k}) \bmu = -2\ff \; , \label{eq:inteq_dir_int}
\end{equation}
for the interior problem.
As noted in~\cref{subsubsec:nullspacecorr}, the standard layer potentials
result in rank-deficient representations for the boundary value problem.
It is well-known that~\cref{eq:inteq_dir_int} has a two dimensional
null-space due to this issue. Thus, proceeding as discussed earlier,
we instead analyze the equation
\begin{equation}
(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
\end{equation}

@@

\begin{thrm}
\label{thm:dlmain}
Suppose that $\Omega$ is a simply connected domain, then the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k$ is 
Dirichlet eigenvalue for Stokes equation on $\Omega$.
\end{thrm}
\begin{proof}
Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-} = (\cI - 2\cD_{k}) \bmu = 0$ on $\Gamma$. 
Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again for the jump in surface traction
for the double layer potential, we conclude that the exterior limit
of the surface traction $\bt^{+} = 0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Sotkes equation in the exterior $E$.
From uniqueness of the Neumann problem in the exterior $E$, we conclude
that $\bu \equiv 0$ in $E$ as well, which in particular implies that
the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k$ is not a Dirichlet
eigenvalue for the Stokes equation on $\Omega$.

>>>>

In this section, we discuss how integral equations
can be used to compute to the Stokes eigenvalues.
%
We closely follow the approach developed by Zhao and Barnett
for computing the Laplace eigenvalues~\cite{zhao2015robust}.
%
They compute the Laplace eigenvalues using the following
steps: 1) represent the solution 
as a layer potential with 
an unknown density, and choose the representation such that
you get a second kind integral equation for the unknown density;
2) establish that the intergral equation is not invertible 
only at the Dirichlet eigenvalues for Laplace's equation;
3) prove that the zeros of the Fredholm determinant 
(when the compact operator is in trace class) 
line up with the Dirichlet eigenvalues; 
4) and finally, show that when the integral equation
is discretized using a Nystr\"{o}m method, the zeros of 
the determinant 
of the discrete linear system 
converge exponentially
to the zeros of the Fredholm determinant.

We adapt their approach for computing the 
Dirichlet eigenvalues for Stokes equation. 
In the context of oscialltory Stokes equation,
while integral representations for the modified
Stokes equation are directly applicable, 
proving invertibility of the associated operators
away from the eigenvalues is a more involved task.
This in turn requires proving uniqueness results
for various interior and exterior boundary value problems
for the oscillatory Stokes equations.
These results play a crucial role in estabilishing step
2 of the Zhao-Barnett approach listed above.
To the best of our knowledge, the uniqueness results, particularly
for exterior domains are new results.

In order to prove the uniqueness results, we follow the 
structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
for the scalar Helmholtz equation.
%
First, we define the interior boundary value problems
of interest, which is straightforward.
%
For the exterior problems, we introduce a radiation condition
for the equations and establish that, under certain assumptions,
the standard layer potentials satisfy the radiation condition.
and define well-posed versions of the
exterior boundary value problems which incorporate the
radiation condition.
%
Then we derive a number of uniqueness
results for many standard boundary value problems.
%
Along with the Fredholm alternative, these uniqueness
results are sufficient to derive the invertibility of appropriate
integral equations for a number of boundary value problems
on simply and multiply connected domains.

Once the equivalence between the non-invertibility
of the second kind integral equation and Dirichlet eigenvalues
for Stokes equations is established,
the details of how the Fredholm determinant can be used as a
numerical tool for computing the Stokes eigenvalues
follows in a straightforward manner from the results 
in~\cite{zhao2015robust}. 
We reproduce the relevant results from their work applied 
in this context for completeness.

@@

Let $\Omega$ be a bounded domain with $C^2$ boundary
denoted by $\Gamma$.
The Dirichlet boundary problem specifies the
velocity of the fluid on the boundary, i.e.

@@

Let $\bsigma$ denote the stress tensor associated with
field $(\bu,p)$. 
Specifying the surface traction, $\bt = \bsigma \cdot \bnu$,
on the boundary gives the Neumann boundary value
problem, i.e.

@@

\begin{thrm}
The oscillatory Stokeslet, as defined in \eqref{eq:ostokeslet}, 
satisfies the radiation condition in Definition \ref{def:radcond}.
Suppose that $\Gamma$ is the boundary of a region $\Omega$
and is $C^{2}$. 
Suppose that $\bmu \in C(\Gamma)$ and satsifies
$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
$\bnu$ dentoes the outward normal to the curve $\Gamma$.
Then, the oscillatory Stokes 
double layer potential $\bD[\bmu]$, as defined in \eqref{eq:doublelayer},
also satisfies the radiation condition.
\end{thrm}

\begin{proof}
Consider the Stokeslet induced by an arbitrary charge
$k^2 \bpsi$ at the origin where $\psi \in \mathbb{C}^2$ 
is a constant. Let $r = |\xx|$,
$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have

@@

\begin{definition}[Exterior Dirichlet problem]
  \label{def:dir_exterior}
  Let $\ff \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:dir_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bu &= \ff \quad \bx \in \Gamma \, , 
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}
\begin{definition}[Exterior Neumann problem]
  \label{def:neu_exterior}  
  Let $\bg \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt &= \bg \quad \bx \in \Gamma \, ,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

@@

\begin{thrm}
  Let $\Omega$ be a bounded domain and suppose that
  $\Im (k) \neq 0$. Then both the interior
  Dirichlet and Neumann boundary value problems have
  unique solutions.
\end{thrm}
\begin{proof}
  A couple applications of the divergence theorem establish
  that
  \begin{equation} \label{eq:greenlike}
    \int_\Omega |2\be(\bu)|^2 - \overline{k}^2 |\bu|^2 \, dV
    = \int_\Gamma \bu \cdot \overline{\bt} \, dS \; . 
  \end{equation}
  Suppose that either $\bu = 0$ or $\bt = 0$ on $\Gamma$.
  Then, the right hand side of \cref{eq:greenlike} is
  zero. 
  Taking the real and imaginary parts of \cref{eq:greenlike},
  it is clear that $\bu \equiv 0$, if $\text{Im}(k) \neq 0$.
\end{proof}

@@

In the next lemma, we prove the analogue of Rellich's lemma for the
oscillatory Stokes equation. 
\begin{lem}
  \label{lem:rellich}
    Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose that $\bu$ satisfies the oscillatory Stokes equation in
  $E$ and that 
\begin{equation}
\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
\, . \label{eq:decayatinf}
\end{equation}
Then each component of $\bu$ is harmonic in $E$.
\end{lem}
\begin{proof}
We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
oscillatory biharmonic equation in $E$, i.e.
\begin{equation}
\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
\end{equation}
For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
j=1,2 \, . \nonumber
\end{equation}
Using Parseval's identity then
\begin{equation}
\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
|a_{2,n}(r)|^2 \, . \nonumber
\end{equation}
Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
\begin{equation}
\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
\end{equation}
Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
the functions $a_{j,n}$ are linear combinations of 
\begin{equation}
r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
n\neq 0 \, , \nonumber
\end{equation}
and
\begin{equation}
1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, ,  \nonumber
\end{equation} 
where $H_{n}^{1,2}(\cdot)$ are the Hankel functions of the first and
second kind of order $n$.
Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$ must be zero. 
Thus, 
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
\, , \nonumber
\end{equation}
for sufficiently large $r$.
Finally, by \cref{cor:analytic}, $\bu$ is
analytic in $E$. Therefore, each $u_j$ is harmonic
throughout $E$.
\end{proof}
\begin{remark} \label{rmk:harmu}
  Note that if $\bu$ satisfies the assumptions
  of~\cref{lem:rellich}, then each component is harmonic
  and thus $\bu$ satisfies
\begin{align}
k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
\nabla \cdot \bu &= 0 \, . \nonumber
\end{align}
Taking the inner product of~\cref{eq:massconsred} with $\nabla^{\perp}$,
we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
and $\nabla \cdot \bu = 0$, i.e. $u_1 - i u_2$ is analytic.
\end{remark}
\begin{remark}
Note that in~\cref{lem:rellich}, $\bu$ need not be a radiating solution. 
All that is assumed of $\bu$ is that it satifies the PDE in $E$.
\end{remark}

@@

\begin{proof}
Since $\bu = 0$ on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{equation}
\lim_{r\to\infty}
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
dV = 0 \nonumber
\end{equation} 
In particular, this implies that
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, . \nonumber
\end{equation}
Thus, the conditions for $\bu$ in~\cref{lem:rellich}
are satisfied, and each component of $\bu$ is a harmonic function
with $\bu \to 0$ as $r \to \infty$. Furthermore, since $\bu=0$ on
$\Gamma$, by the uniqueness of solutions to the
Dirichlet problem for Laplace's equation
on exterior domains, we conclude that $\bu \equiv 0$ in $E$.
\end{proof}

@@

\begin{proof}
Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = i\eta \bu$
on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{align*}
0 &=
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
&= 
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad + 2 \left( (k_{1}\eta_{1} + k_{2}\eta_{2}) \int_{\Gamma} |\bu|^{2} dS  \right)
\, .
\end{align*}
Because all of the quantities in the last expression above are
nonnegative, we have that
\begin{equation}
  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, .
  \nonumber
\end{equation}
The result then follows from the uniqueness of solutions to the exterior
Dirichlet problem.
\end{proof}

@@

We analyze two different representations for the Dirichlet problem---
when the velocity is represented using a double layer potential,
i.e. setting $\bu=\bD_{k} \bmu$, and when the velocity
is represented using a mixed layer potential,
i.e. setting $\bu=(i\eta \bS_{k} + \bD_{k})\bmu$, where in both cases $\bmu$ 
is the unknown density to be solved for. 
Even though both reprensentations result in a second kind
Fredholm integral equation for the Dirichlet problem,
the spectral properties of these representations are very
different based on the genus of the domain.
We analyze the double layer potential representation 
in~\cref{subsec:dlanalysis}
and the mixed layer potential representation in~\cref{subsec:mixedanalysis}.

\begin{remark}
The analysis of integral equations for the oscillatory Stokes
equation and the correspondance betweeen its null spaces and the eigenvalues
of Stokes equation is analogous to the analysis carried out
for integral equations for Helmholtz equation and the eigenvalues
for the Laplace equation in~\cite{zhao2015robust}.
$\bu$ plays the role of the Dirichlet data, and $\bt$ plays the role
of the Neumann data. 
Once the Green's representation and uniqueness results for the 
the oscillatory Stokes equation have been established,
the remainder of the analysis of the integral equations
is in spirit identical to the analysis presented in~\cite{zhao2015robust}.
\end{remark}

\subsubsection{Double layer reprensentation}
\label{subsec:dlanalysis}
Suppose that the solution to the Dirichlet problem using
a double layer potential defined on $\Gamma$, i.e.
setting $\bu = \bD_{k} \bmu$ for
an unknown density $\bmu$. 
Substituting this representation
into the Dirichlet boundary condition and applying
\cref{lem:jump-conds}, we obtain

\begin{equation}
  (\cI - 2\cD_{k}) \bmu = -2\ff \; , \label{eq:inteq_dir_int}
\end{equation}
for the interior problem.
As noted in~\cref{subsubsec:nullspacecorr}, the standard layer potentials
result in rank-deficient representations for the boundary value problem.
It is well-known that~\cref{eq:inteq_dir_int} has a one dimensional
null-space due to this issue. Thus, proceeding as discussed earlier,
we instead analyze the equation
\begin{equation}
(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
\end{equation}

@@

\begin{thrm}
\label{thm:dlmain}
Suppose that $\Omega$ is a simply connected domain, then the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k$ is 
Dirichlet eigenvalue for Stokes equation on $\Omega$.
\end{thrm}
\begin{proof}
Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-} = (\cI - 2\cD_{k}) \bmu = 0$ on $\Gamma$. 
Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again for the jump in surface traction
for the double layer potential, we conclude that the exterior limit
of the surface traction $\bt^{+} = 0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Sotkes equation in the exterior $E$, since
$\cW[\mu] = 0$ implies $\int_{\Gamma} \mu \cdot \bnu = 0$.
From uniqueness of the Neumann problem in the exterior $E$, we conclude
that $\bu \equiv 0$ in $E$ as well, which in particular implies that
the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k$ is not a Dirichlet
eigenvalue for the Stokes equation on $\Omega$.

From Green's representation for the oscillatory Stokes qeuation, 
we know that 
  \begin{equation} \label{eq:rep-theorem}
    \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \Omega^{C} \; .
    \end{cases}
  \end{equation}
Suppose that $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
and let $\bu$ denote the corresponding eigenfunction, and let $\bt^{-}$ denote
the surface traction associated with the eigenfunction on the boundary $\Gamma$.
Since $\bu$ is a Dirichlet eigenfunction, the velocity restricted to the boundary
$\bu^{-} = 0$. 
Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
its derivative on $\Gamma$ using~\cref{lem:jump-conds}, we get
\begin{equation}
\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, ,\implies \left(\cI - 2\cDt_{k} \right) 
\bt^{-} = 0 \, .
\end{equation}
From the Fredholm alternative, it then follows that $(\cI - 2\cD_{k})$ has a non-trivial 
null-space.
However, we need to prove that $(\cI -2\cD_{k} - 2\cW)$ has a non-trivial null-space
for which we need the following two lemmas.
